Illusion Game & PCS

### 2025-04-21 analysis/1_cleaning.qmd
minor
changes to analysis scripts

data_ppt <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGamePhenomenologicalControl/refs/heads/main/data/rawdata_participants.csv")

@@

>>>>

# data_ppt <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGamePhenomenologicalControl/refs/heads/main/data/rawdata_participants.csv")

data_ppt <- read.csv("C:/Users/asf25/Desktop/studies/IllusionGamePhenomenologicalControl/data/rawdata_participants.csv")

@@

### PCS

pcs <-  select(data_ppt, starts_with("pcs_"))

data_ppt$pcs_tastescore <- rowMeans(pcs[grepl("taste", names(pcs))])

data_ppt$pcs_postsessionsuggetsion <- sqrt(data_ppt$pcs_urgepress * data_ppt$pcs_memorypress)

#delete with more participants (changes have been made in script)
pcs <- pcs |>
  rename(pcs_amnesia = pcs_rememeber)

# data_ppt$pcs <- rowMeans(pcs[grepl("hands|music|mosquito|tastescore|arm|negative|postsession|amnesia(?!_w)", names(pcs))], na.rm = TRUE)

data_ppt$pcs <- rowMeans(pcs[!grepl("pcs_amnesia_w", names(pcs)) & grepl("hands|music|mosquito|tastescore|arm|negative|postsession|amnesia", names(pcs))], na.rm = TRUE)

data_ppt$pcs_SD <- sd(data_ppt$pcs, na.rm = TRUE)
```
